---
title: "Reproducible Document"
author: "rostools" 
format: html
---

```{r setup}
#| message: false
#| warning: false


library(tidyverse)

post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))

small_post_meal_data <- select(post_meal_data, id, Age, BMI, Group, auc_pg, auc_ins, glykemi)

tidier_post_meal_data <- small_post_meal_data %>%
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  ) %>%
  filter(glykemi == 0) %>%
  select(-glykemi)

tidied_post_meal_data <- tidier_post_meal_data %>%
  mutate(
    insulin_glucose_ratio = auc_insulin / auc_glucose,
    Group = if_else(Group == "CTR", "Control", "First-degree relative")
  )
```

## Writing R code

2 + 2

```{r}
2 + 2
```
## About me
- Sarah
- Affiliated at The Parker Institute, Bispebjerg og Frederikberg Hospitaler
- Københavns Universitet
**Jeg er ph.d.-studerende på 2. år**
*Jeg bor i København*

## Simple code
```{r}
3 * 3
```
## Testing for Git 

hej, det er koldt 

## Showing the data
```{r}
post_meal_data

glimpse(post_meal_data)
```
## Plot one continuous variable
```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

See @fig-bmi-histo

## Exercise: dscrete plots
```{r}
#| fig-cap: "Group distribution"
#| label: fig-group-bar
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```

See @fig-group-bar

See @fig-group-bar above for a cool plot!

## Plotting two discrete variables


```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar()
```
```{r}
ggplot(post_meal_data, aes(x = Group, fill = as.character(glykemi))) +
  geom_bar(position = position_dodge())
```
## Side by side plots
```{r}
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```
```{r figure-bmi-glycemia}
#| fig-cap: "BMI and glycemia, side by side"
#| fig-subcap:
#|   - "Distribution of BMI."
#|   - "Number of those with glycemia"
#| layout-ncol: 2
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
ggplot(post_meal_data, aes(x = glykemi)) +
  geom_bar()
```

## Plotting two continuous variables
```{r}
#| fig-cap: "Scatterplot of BMI and the area under the curve for glucose"
#| label: fig-bmi-auc-pg
ggplot(post_meal_data, aes(x = BMI, y = auc_pg)) +
  geom_point() +
  geom_smooth()
```
## Selecting data

```{r}
select(post_meal_data, Age)
```
```{r}
select(post_meal_data, Age)

select(post_meal_data, Age, BMI, Weight)
```
```{r}
select(post_meal_data, Age)

select(post_meal_data, Age, BMI, Weight)

select(post_meal_data, -Group)
```

```{r}
select(post_meal_data, Age)

select(post_meal_data, Age, BMI, Weight)

select(post_meal_data, -Group)

select(post_meal_data, starts_with("PG"))
```
```{r}
select(post_meal_data, Age)

select(post_meal_data, Age, BMI, Weight)

select(post_meal_data, -Group)

select(post_meal_data, ends_with("DXA"))
```
```{r}
select(post_meal_data, Age)

select(post_meal_data, Age, BMI, Weight)

select(post_meal_data, -Group)

select(post_meal_data, ends_with("DXA"))

select(post_meal_data, contains("0"))
```
## Renaming Columns

```{r}
small_post_meal_data %>%
  rename(auc_glucose = auc_pg)
```
```{r}
small_post_meal_data %>%
  rename(
    auc_glucose = auc_pg,
    auc_insulin = auc_ins
  )
```

# Task 1.
```{r}
post_meal_data %>%
  select(contains("OGTT"))
```

# Task 2.
```{r}
post_meal_data %>%
  select(contains(".."), -contains(".."))
```

# Task 3.
```{r}
post_meal_data |>
  rename(
    P.Glucose.minus5.OGTT = P.Glucose..5.OGTT,
    Insulin.minus.5.OGTTX = Insulin..5.OGTT.X
  )
```


# Task 4.
```{r}
post_meal_data |>
  select(id, BMI, Length, Weight, Age) |>
  rename(Height = Length)
```

## Filtering data
```{r}
small_post_meal_data %>%
  filter(glykemi == 1)
```
```{r}
small_post_meal_data %>%
  filter(glykemi == 1)

small_post_meal_data %>%
  filter(BMI >= 25)
```
```{r}
small_post_meal_data %>%
  filter(glykemi == 1)

small_post_meal_data %>%
  filter(BMI >= 25)

small_post_meal_data %>%
  filter(Group == "CTR")
```
```{r}
small_post_meal_data %>%
  filter(glykemi == 1)

small_post_meal_data %>%
  filter(BMI >= 25)

small_post_meal_data %>%
  filter(Group == "CTR")

small_post_meal_data %>%
  filter(Group == "CTR" | BMI >= 25)
```

## Modifying data

```{r}
tidier_post_meal_data %>%
  mutate(insulin_glucose_ratio = auc_insulin / auc_glucose)

tidier_post_meal_data %>%
  mutate(
    insulin_glucose_ratio = auc_insulin / auc_glucose,
    Group = if_else(Group == "CTR", "Control", "First-degree relative")
  )
```

## Practise with filter and mutate
```{r}
# Task 1.
post_meal_data %>%
  filter(BMI >= 25 & BMI <= 40 & Group == "FDR")

# Task 2.
post_meal_data %>%
  mutate(
    percent_body_fat = (Fat.mass.DXA / Weight) * 100
  ) %>%
  filter(percent_body_fat > 30)
```

## Visualizing with a jitter plot

```{r}
tidied_post_meal_data %>%
  mutate(overweight = if_else(BMI >= 25, "Overweight", "Not overweight")) %>%
  ggplot(aes(x = overweight, y = insulin_glucose_ratio)) +
  geom_jitter()
```
```{r}
tidied_post_meal_data %>%
  mutate(overweight = if_else(BMI >= 25, "Overweight", "Not overweight")) %>%
  ggplot(aes(x = overweight, y = insulin_glucose_ratio)) +
  geom_boxplot()
```
```{r}
tidied_post_meal_data %>%
  mutate(overweight = if_else(BMI >= 25, "Overweight", "Not overweight")) %>%
  ggplot(aes(x = overweight, y = insulin_glucose_ratio)) +
  geom_violin()
```
```{r}
tidied_post_meal_data %>%
  mutate(overweight = if_else(BMI >= 25, "Overweight", "Not overweight")) %>%
  ggplot(aes(x = overweight, y = insulin_glucose_ratio)) +
  geom_jitter()
```
## Plotting three or more variables
```{r}
tidied_post_meal_data %>%
  filter(BMI < 30) %>%
  ggplot(aes(x = Age, y = auc_insulin, colour = Group)) +
  geom_point()
```
```{r}
tidied_post_meal_data %>%
  filter(BMI < 30) %>%
  mutate(young = if_else(Age < 40, "Young", "Old")) %>%
  ggplot(aes(x = Age, y = auc_insulin, colour = Group)) +
  geom_point() +
  facet_grid(cols = vars(young))
```
```{r}
tidied_post_meal_data %>%
  filter(BMI < 30) %>%
  mutate(young = if_else(Age < 40, "Young", "Old")) %>%
  ggplot(aes(x = BMI, y = auc_insulin, colour = Group)) +
  geom_point() +
  facet_grid(cols = vars(young))
```
```{r}
tidied_post_meal_data %>%
  filter(BMI < 30) %>%
  mutate(young = if_else(Age < 40, "Young", "Old")) %>%
  ggplot(aes(x = BMI, y = auc_insulin, colour = Group)) +
  geom_point() +
  facet_grid(rows = vars(young))
```
```{r}
tidied_post_meal_data %>%
  filter(BMI < 30) %>%
  mutate(young = if_else(Age < 40, "Young", "Old")) %>%
  ggplot(aes(x = BMI, y = insulin_glucose_ratio, colour = Group)) +
  geom_point() +
  facet_grid(rows = vars(young)) +
  labs(
    x = "Body Mass Index (BMI)",
    y = "Insulin to glucose ratio"
  )
```
