---
title: "Reproducible Document"
author: "rostools" 
format: html
---

```{r setup}
#| message: false
#| warning: false



library(tidyverse)

post_meal_data <- read_csv2(here::here("data/post-meal-insulin.csv"))
```

## Writing R code

2 + 2

```{r}
2 +2 
```
## About me
- Sarah
- Affiliated at The Parker Institute, Bispebjerg og Frederikberg Hospitaler
- Københavns Universitet
**Jeg er ph.d.-studerende på 2. år**
*Jeg bor i København*

## Simple code
```{r}
3*3
```
## Testing for Git 

hej, det er koldt 

## Showing the data
```{r}
post_meal_data

glimpse(post_meal_data)
```
## Plot one continuous variable
```{r}
#| fig-cap: "Distribution of BMI"
#| label: fig-bmi-histo
ggplot(post_meal_data, aes(x = BMI)) +
  geom_histogram()
```

See @fig-bmi-histo

## Exercise: dscrete plots
```{r}
#| fig-cap: "Group distribution"
#| label: fig-group-bar
ggplot(post_meal_data, aes(x = Group)) +
  geom_bar()
```
---
See @fig-group-bar

See @fig-group-bar above for a cool plot!

## Plotting two discrete variables
```
```

```{r}
ggplot(post_meal_data, aes(x= Group, fill= as.character(glykemi))) + geom_bar()
```
```{r}
ggplot(post_meal_data, aes(x= Group, fill= as.character(glykemi))) + geom_bar(position= position_dodge())
```
## Side by side plots
```{r}
ggplot(post_meal_data, aes(x=BMI)) + geom_histogram()
ggplot(post_meal_data, aes(x=glykemi)) + geom_bar()
```
```{r figure-bmi-glycemia}
#| fig-cap: "BMI and glycemia, side by side"
#| fig-subcap: 
#|   - "Distribution of BMI."
#|   - "Number of those with glycemia"
#| layout-ncol: 2 
ggplot(post_meal_data, aes(x=BMI)) + geom_histogram()
ggplot(post_meal_data, aes(x=glykemi)) + geom_bar()
```
